\chapter*{Acknowledgements}
I would like to express my sincerest sense of gratitude to my supervisors Prof.
Dietrich Klakow and Prof. Iryna Gurevych. Not only that they were always open to
my questions and were extremely helpful to form the direction of my research,
but I appreciate them for many opportunities they gave me to work,
teach,research and help me to survive through last two years.

Dietrich was not only a supervisor for me but was a friend, always supporting me
for any problem I had in academy or life in Saarbr\"{u}cken. I consider being his
teaching assistant as a once-in-a-life opportunity which made re-gain my confidence and
brought hope and discipline back to my life. I also met Benjamin Roth in
Dietrich's LSV lab. for the first time. His big influence on this work and his
aids for more than a year made this work happened.

It was a tremendous 8 months of work and research in UKP lab.
in Darmstad during my internship there. A very professional and disciplinary
atmosphere of Iryna's lab. let me experience the true taste of firm German
working spirit. During that time, I met Dr. Jungi Kim, one of the kindest and
sharpest researchers I have ever met. Jungi was literally always there to answer
my questions both in theoretical and technical matters, to give ideas, to help
me to shape my research. Without him it was impossible to finish this work. Dr.
Judith Eckle-Kohler and Silvana Hartmann helped me a lot to learn how to work
with Uby and provide extensive information on the details of lexical resources I
used in this work. I shall not forget to thank Jinseok Nam for his tutorials on
deep learning in our weekly reading group.

It was always pleasant to talk to Ivan Titov and Chris Biemann
and receive their comments and guidance on my thesis, specially Ivan who shaped
the structure of researching on machine learning during his amazing seminars.
Even though I have not yet met Sebastian Riedel and Antoine Bordes in person but it was
always joyful to receive their extensive and useful replies to any question I
asked them via email.

I can claim I managed to find my friends in CoLi. Liling showed me how to be
a useful person to your world  while you are drown in papers and works, he is
one of the reasons that I chose this topic for my work and long-time discussions
with him was more useful than many papers or books I ever read. Mariona, Wei
Qiu and Jesus were more than just a friend for me and we became a family during
the master program in CoLi.

It doesn't matter how far you are living from your parents, they always radiate
love and support across oceans to you. In my case, I am thankful to their truly
unconditional love for every second of my life. 

Studying in CoLi not only gave me a research direction to work on it but also
gave me the chance to meet my true love, Beata. Working, studying, travelling
and in one word, living with her is beyond what I could have expected from life.




\newpage

\section*{Eidesstattliche Erkl\"{a}rung}
Hiermit erkl\"{a}re ich, dass ich die vorliegende Arbeit selbstst\"{a}ndig
verfasst und keine anderen als die angegebenen Quellen und Hilfsmittel
verwendet habe.

\vspace{2cm}
\section*{Declaration}
I hereby confirm that the thesis presented here is my own work, with all
assistance acknowledged.


\vspace{4cm}
Saarbr\"{u}cken, 4th December 2013\\
Ehsan Khoddammohammadi 
